\chapter{Literature review}
\label{chp:literature_review}

For this work, we will be exploring a subset of \gls{ai} models know as compositional neural network models.
We will select a model of this type by exploring and discussing three such models, choosing one with which to proceed.
These models, while not the state-of-the-art as of the time of planning this work, will be some of the more noteworthy models of this subset and will have had a notable influence on successive models.
Additional models of this type will also be explored to see how they have been expanded and improved upon.
We will also explore the datasets used by the models down below, determining the characteristics of the datasets, their strengths, and any observed drawbacks.
Finally, we will round off with a comparison between the different \gls{ml} tasks explored, the datasets that target these tasks, and the characteristics of the models covered (specifically those details attributed to their compositional nature).

\input{content/chapters/literature_review/datasets/datasets}
\clearpage

\input{content/chapters/literature_review/choosing_the_compositional_model/choosing_the_compositional_model}
\clearpage

\input{content/chapters/literature_review/other_compositional_models/other_compositional_models.tex}
\clearpage

\input{content/chapters/literature_review/discussion/discussion.tex}
\clearpage

\section{Conclusion}
\label{sec:literature_review_conclusion}

In this literature review, we have explored a selection of models and datasets designed to solve \gls{ml} visual/language tasks.
We have also touched on the \gls{vcr} task which will be tackled by this work.
In the following chapters, we will discuss how the model was adapted to work on the \gls{vcr} task and dataset, the experiments and setups for evaluating on \gls{vcr}, the ablations done, and conclude with a discussion of future work.
